Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2015-08-28 doc/GMP2015/revision_3/s04_recombination.tex
Revision 3, close to finished.

The main barrier in recombination when given an optimal DR-plan  (of smallest possible size or max fan-in) for a system $S$,  is that the number of children of the root  (resp. number of roots of the DR-plan)---and correspondingly the  size and complexity of the (indecomposable) algebraic system $I$ to be solved---could be arbitrarily large as a function of the size of $S$. This difficulty can persist even after optimal parametrization of the indecomposable system $I$ as in \cite{sitharam2010optimized} to minimize its algebraic complexity.

@@

\begin{enumerate}[(a)]
    \item
    {\sl Small DR-plan.}
    We obtain a  parameterized family of systems $I_{\lambda_F}$---one for each value $\lambda_F$ for the parameters $F$,  all of which have small DR-plans. Thus, given a value $v$ for $\lambda_F$, the system $I_v$ can potentially be solved or realized easily once the orientation type of the solution is known  (when the DR-plan size is small enough).

@@

\subsection{Optimized Modification by Enlarging the Class of Reduced
Graphs}
\label{sec:tdecomp}
%
It is possible in principle to decrease $k$ for a OMD$_k$ graph (i.e.\ the number of edges to be removed to ensure an isostatic completion that is decomposable with a small DR-plan) by considering reduced graphs $G'$ (and modified graphs $H$) that come from a larger class than partial 2-trees but nevertheless have convex Cayley configuration spaces at least when the realization space is restricted to a sufficiently comprehensive orientation type. In particular, the so-called \dfn{tree-decomposable graphs of low Cayley complexity} \cite{sitharam2011cayleyI,sitharam2011cayleyII} include the partial 2-trees and many others that are not partial 2-trees. See an illustration in Figure \ref{fig:omd_k33_example}. These too result in DR-plans of size 2 or 3, putting $G$ in the class OMD$_k$ and thus meeting Criteria (a) and (b). The Criterion (c) is met---for example when $k=1$---because 1-dof Cayley configuration spaces of linkages based on such graphs $G'$ are known to be single intervals when a comprehensive orientation type $\sigma_p$ of the sought solution $p$ is given. In addition, the bounds of these intervals are of low algebraic complexity. More precisely, the bounds  can themselves be computed using a DR-plan of size 2 or 3, i.e.\ the computation of these bounds is tree-decomposable. Alternatively, the bounds are in a simple quadratic or radically solvable extension field over the rationals, or they can be computed by solving a triangularized system of quadratics.

>>>>

The main barrier in recombination when given an optimal DR-plan  (of smallest possible size or max fan-in) for a system $S$,  is that the number of children of the root  (resp. number of roots of the DR-plan) -- and correspondingly the  size and complexity of the (indecomposable) algebraic system $I$ to be solved -- could be arbitrarily large as a function of the size of $S$. This difficulty can persist even after optimal parametrization of the indecomposable system $I$ as in \cite{sitharam2010optimized} to minimize its algebraic complexity.

@@

\begin{enumerate}[(a)]
    \item
    {\sl Small DR-plan.}
    We obtain a  parameterized family of systems $I_{\lambda_F}$ -- one for each value $\lambda_F$ for the parameters $F$,  all of which have small DR-plans. Thus, given a value $v$ for $\lambda_F$, the system $I_v$ can potentially be solved or realized easily once the orientation type of the solution is known  (when the DR-plan size is small enough).

@@

\subsection{Optimized Modification by Enlarging the Class of Reduced
Graphs}
\label{sec:tdecomp}
%
It is possible in principle to decrease $k$ for a OMD$_k$ graph (i.e.\ the number of edges to be removed to ensure an isostatic completion that is decomposable with a small DR-plan) by considering reduced graphs $G'$ (and modified graphs $H$) that come from a larger class than partial 2-trees but nevertheless have convex Cayley configuration spaces at least when the realization space is restricted to a sufficiently comprehensive orientation type. In particular, the so-called \dfn{tree-decomposable graphs of low Cayley complexity} \cite{sitharam2011cayleyI,sitharam2011cayleyII} include the partial 2-trees and many others that are not partial 2-trees. See an illustration in Figure \ref{fig:omd_k33_example}. These too result in DR-plans of size 2 or 3, putting $G$ in the class OMD$_k$ and thus meeting Criteria (a) and (b). The Criterion (c) is met -- for example when $k=1$ -- because 1-dof Cayley configuration spaces of linkages based on such graphs $G'$ are known to be single intervals when a comprehensive orientation type $\sigma_p$ of the sought solution $p$ is given. In addition, the bounds of these intervals are of low algebraic complexity. More precisely, the bounds  can themselves be computed using a DR-plan of size 2 or 3, i.e.\ the computation of these bounds is tree-decomposable. Alternatively, the bounds are in a simple quadratic or radically solvable extension field over the rationals, or they can be computed by solving a triangularized system of quadratics.

### 2015-08-28 doc/GMP2015/revision_3/s05_problems.tex
Revision 3, close to finished.

\subsubsection{Special Classes of Small DR-Plans}
As seen in the previous section, 2-trees and tree-decomposable graphs have not only small, but also special DR-plans that permit easy solving---essentially by solving a single quadratic at a time.

>>>>

\subsubsection{Special Classes of Small DR-Plans}
As seen in the previous section, 2-trees and tree-decomposable graphs have not only small, but also special DR-plans that permit easy solving -- essentially by solving a single quadratic at a time.
